\documentclass[12pt, a4paper]{article}
\usepackage{ctex}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[margin = 1in]{geometry}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{ifthen}
\usepackage{syntonly}
\usepackage{color}
\usepackage{makecell}
\usepackage{eufrak}
\usepackage{comment}
\usepackage[bitstream-charter]{mathdesign}
\usepackage[T1]{fontenc}
\usepackage[colorlinks, CJKbookmarks=true, linkcolor=black, anchorcolor=blue, citecolor=blue]{hyperref}
\pagestyle{fancy}

%\fancyhf{} % sets both header and footer to nothing
\lhead{}
\chead{}
\rhead{}
\renewcommand{\headrulewidth}{0pt}

\renewcommand\contentsname{Contents}
\renewcommand\refname{References}
\renewcommand\figurename{Fig.}
\newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}}

\newcounter{footnotesintable}

\begin{document}

\title{Project Report of MxStar Compiler\\\begin{large}(Course Project of Compiler)\end{large}}
\author{Weixin Deng {\kaishu{(邓伟信})}\\ACM Class, Shanghai Jiao Tong University}
\date{}

\maketitle

\section{Introduction}

This project is a compiler of MxStar\upcite{MxStar} language(a combination of C and Java), implemented in Java. The GitHub repository of my project is: \url{https://github.com/dengwxn/Mx-Compiler}.

\section{Implementation}

\begin{table}[!hbp]
	\centering
	\begin{tabular}{|l|l|}
	\hline
	Source Language        & MxStar      \\ \hline
	Target Language        & x86-64 NASM \\ \hline
	Lexer/Parser Generator & antlr4      \\ \hline
	\end{tabular}
\end{table}

\subsection{IR Generation}

\paragraph{Logical Expressions}
I do not use {\ttfamily set} instruction when dealing with logical expressions. Instead, I maintain two blocks {\ttfamily logicTrue} and {\ttfamily logicFalse} as the logic exit blocks. In {\ttfamily assign} statements, I add {\ttfamily mov 0/1} accordingly. Otherwise in {\ttfamily if} statements, {\ttfamily thenStmt} generate IR in {\ttfamily logicTrue} and    {\ttfamily elseStmt} in {\ttfamily logicFalse}.

\subsection{Optimization}

\begin{itemize}
	\item 
	Global constant propagation.
	\item 
	Global copy propagation.
	\item
	Dead code elimination using neededness analysis.
	\begin{itemize}
		\item Remove unneeded instructions.
		\item Remove empty blocks.
		\item Remove unreachable blocks.
		\item Remove some useless loops using a conservative strategy.
		\item
		Compress {\ttfamily jump} when jumping to a block consisting of a {\ttfamily jump} instruction.
	\end{itemize}
	\item
	Function inlining.
	\item 
	Global variable loading. 
	\begin{itemize}
		\item 
		Load them in the beginning of a function and store back in the end.
		\item
		Extra storing and loading might be needed when having {\ttfamily call}.
	\end{itemize}
	\item 
	Value numbering on extended basic blocks.
	\item 
	Strength reduction.
	\item
	Chordal graph coloring. 
	\begin{itemize}
		\item 
		Although I do not convert my program to SSA, the result of register allocation is not bad.
	\end{itemize}
\end{itemize}

\section{Discussions}

\paragraph{Debug}
I use gdb to debug the assembly code. The complete script to support gdb is {\ttfamily nasm -felf64 prog.asm -gdwarf \&\& gcc prog.o -o prog -g -no-pie}.

\paragraph{Object Oriented Programming}
My implementation is far away from OOP style. I think using OOP will make the whole project clearer but also make it harder to code.

\section{Appendix}

\begin{thebibliography}{9}
  \bibitem{MxStar}
	MxStar Language Manual.
	\\\url{https://acm.sjtu.edu.cn/w/images/3/30/M_language_manual.pdf}.
  \bibitem{CMU}
  	CMU 15-411 Compiler Design.
	\\\url{http://www.cs.cmu.edu/~janh/courses/411/18/schedule.html}.
  \bibitem{Stanford} 
	Stanford CS143 Compilers.
	\\\url{http://web.stanford.edu/class/cs143/index2018.html}.
  \bibitem{LianminZheng}
	Lianmin Zheng's Compiler project.
	\\\url{https://github.com/merrymercy/compiler2017/blob/master/doc/report.pdf}.
  \bibitem{ZhekaiZhang}
	Zhekai Zhang's Compiler project.
	\\\url{https://github.com/sxtyzhangzk/MxCompiler/blob/master/slide.pdf}.
  \bibitem{HowTo}
  	青木峰郎. 
  	\emph{自制编译器},
  	人民邮电出版社, 2016.
  \end{thebibliography}

\end{document}